Scaffolder - Simple and reproducible genome scaffolding using text configuration files.

### 2011-01-13 text/src/article.tex
Revise abstract

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is piece separate contigs together and fill gaps generated by PCR. This
  scaffolding step however is non-trivial requiring manipulation of large
  blocks of nucleotide sequence. Manually joining contigs also hides the source
  of each region in the final genome fasta file. Taken together these
  considerations make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined "Scaffolder" is implemented in
  the ruby programming language and installed via the RubyGems software
  management system. Genome scaffolds are defined using YAML - a markup
  language which is both human and machine readable. Command line binaries and
  extensive documentation are also available for the package.

>>>>

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is piece separate contigs together and fill gaps generated by PCR. This
  scaffolding step, however, is non-trivial requiring manipulation of large
  blocks of nucleotide sequence. Manually joining contigs also hides the source
  of each region in the final genome fasta file. Taken together these
  considerations make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined "Scaffolder" is implemented in
  the ruby programming language and installed via the RubyGems software
  management system. Genome scaffolds are defined using YAML - a markup
  language, which is both human and machine-readable. Command line binaries and
  extensive documentation are also available for the package.
